I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-12-30 submission/paper.tex
First draft of discussion section.

\subsection{Identifying flood-prone areas}
Table \ref{tab:stormsurge} contains the total projected storm surges for Esbjerg, corresponding to the 20-year and 100-year historical surges, with and without sea level rise. We see that the historical maximum 433 cm is very likely to be exceeded by 2100.

@@

Figure \ref{fig:esbjerg} shows flooding maps corresponding to the entries in Table \ref{tab:stormsurge}. These maps can be used to further develop adaptation policies for Esbjerg.
\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.9\linewidth]{Floodmaps_Harbour.png}
\caption{Flood extents and depths for the city of Esbjerg in year 2100 during storm surges with a 20 year return period (upper row) and a 100 year return period (lower row) with (a) no sea level rise and with sea level rise corresponding to RCP 85 (5th percentile (b), median (c) and 90th percentile (d). }
\label{fig:esbjerg}
\end{center}
\end{figure}

@@

\section{Conclusions and discussion}
\label{disc}

Important to continue an iterative and interactive with end-users, as the decision framework provides actionable information to decision-makers, who will then make their own decisions. These decision are then incorporated into the current adaptation strategy. Continued loop to identify potential vulnerabilities of the approaches across a wide-range of possible futures.

Take home message

\begin{itemize}
\item It is possible to account for uncertainty even if you do a light touch decision-making approach -- Explain what it implies if you don't account and if you do
\item Proof of concept -- connect in a probabilistic way (normally done in a discrete way) -- consider uncertainty in both ways
\item Improve the accessibility and demonstrating the general applicability of policy first approaches -- towards more generic toolkit
\end{itemize}

>>>>

\subsection{Identifying flood-prone areas}
Table \ref{tab:stormsurge} contains the total projected storm surges for Esbjerg, corresponding to the 20-year and 100-year historical surges, with and without sea level rise. We see that using our projections the historical maximum 433 cm is almost certain to be exceeded by 2100.

@@

Figure \ref{fig:esbjerg} shows flooding maps corresponding to the entries in Table \ref{tab:stormsurge}. These maps can be used to further develop adaptation policies for Esbjerg.
\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=\linewidth]{Floodmaps_Harbour.png}
\caption{Flood extents and depths for the city of Esbjerg in year 2100 during storm surges with a 20 year return period (upper row) and a 100 year return period (lower row) with (a) no sea level rise and with sea level rise corresponding to RCP 85 (5th percentile (b), median (c) and 95th percentile (d). }
\label{fig:esbjerg}
\end{center}
\end{figure}

@@

\section{Conclusions and discussion}
\label{disc}
Our case studies demonstrate that it is possible to take uncertainty into account in deciding when and where to implement adaptation measures, even if one uses a light touch decision-making approach. If one fails to do so, bad scenarios, such as 95th percentiles, can be a order of magnitude worse than what the planners are expecting. It is likely worthwhile to be pessimistic in the planning and in the projections.

We consider our case studies proofs of concept, which will be first steps in a sequence of interactions with local planners and other end-users.This has to be an iterative and interactive process, as the decision framework provides actionable information to decision-makers, who will then make their own decisions. These decision can then be incorporated into the current adaptation strategy. Further simulation studies allow a continued loop to identify potential vulnerabilities of the approaches across a wide range of possible futures.

Down the line we plan to develop a flexible and easy-to-use tool kit for decision-making under uncertainty regarding sea level rise. An initial step in this direction is the software used in this analysis, which is publicly available and using free software.
